ABC - HTW Fits

### 2023-12-01 Model/abc_fit.qmd
abc fitting

generate_prior_c_lr <- function(n) {
  prior_samples <- tibble(
    c = runif(n, 0.000001, 5),
    lr = runif(n, 0.000001, 5),
  )
  return(prior_samples)
}

@@

  # Extract target data
  target_data_train_test <- data[expMode2 %in% c("Test", "Train"), ]$y
  target_data_test <- data[expMode2 == "Test", ]$y

@@

  # Return results
  tibble::lst(abc_train_test = abc_train_test, abc_test = abc_test, data=data,n_prior_samples,prior_samples,tol, simulation_function, targets=tibble::lst(target_data_train_test, target_data_test))
}

# Example usage for different models
n_priors=200000
abc_results_varied_exam <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_exam, n_prior_samples = n_priors)
abc_results_varied_alt_exam <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_alt_exam, n_prior_samples = n_priors)
abc_results_varied_alm <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_alm, n_prior_samples = n_priors)

>>>>

generate_prior_c_lr <- function(n) {
  prior_samples <- tibble(
    c = runif(n, 0.000001, 7),
    lr = runif(n, 0.000001, 7),
  )
  return(prior_samples)
}

@@

  # Extract target data
  target_data_train_test <- data[expMode2 %in% c("Test", "Train"), ]$y
  target_data_test <- data[expMode2 == "Test", ]$y
  target_data_train <- data[expMode2 == "Train", ]$y

@@

    # ABC for test data only
  abc_train <- abc(
    target = target_data_train,
    param = prior_samples,
    sumstat = do.call(rbind, simulation_results[1:84, ]),
    tol = tol,
    method = "rejection"
  )

  # Return results
  tibble::lst(abc_train_test = abc_train_test, abc_test = abc_test, abc_train,data=data,n_prior_samples,prior_samples,tol, simulation_function, targets=tibble::lst(target_data_train_test, target_data_test))
}

# Example usage for different models
n_priors=200
abc_results_varied_exam <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_exam, n_prior_samples = n_priors)
abc_results_varied_alt_exam <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_alt_exam, n_prior_samples = n_priors)
abc_results_varied_alm <- run_abc_fits(avg_dsv, input_layer, output_layer, full_sim_alm, n_prior_samples = n_priors)
